---
title: "Blood pressure control, 2017 ACC/AHA definition"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Blood pressure control, 2017 ACC/AHA definition}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.height = 6,
  fig.width = 7.9,
  echo = FALSE
)
```

```{r setup}
library(cardioStatsUSA)
```

## Who is included in this analysis

adults with hypertension according to the 2017 ACC/AHA blood pressure (BP) guideline, defined by any of the following three conditions:

- Systolic BP ≥ 130 mm Hg
- Diastolic BP ≥ 80 mm Hg
- Self-reported use of antihypertensive medication

## BP control (ACC/AHA BP guideline definition)

According to the 2017 American College of Cardiology and American Heart Association (ACC/AHA) Guideline for the Prevention, Detection, Evaluation, and Management of High BP, BP control is defined as having systolic BP < 130 mm Hg and diastolic BP < 80 mm Hg.

### Proportion with BP control by calendar year.

```{r}
nhanes_visualize(outcome = 'bp_control_accaha', 
                 subset_variables = list("htn_accaha", "demo_pregnant"),
                 subset_values = list("Yes", c("No", "Missing")),
                 years = 'all')[[1]]
```

### Proportion with BP control by age group in 2017-2020.

```{r}

nhanes_visualize(outcome = 'bp_control_accaha', 
                 exposure = 'demo_age_cat',
                 subset_variables = list("htn_accaha", "demo_pregnant"),
                 subset_values = list("Yes", c("No", "Missing")),
                 years = 'most_recent')[[1]]
```

### Proportion with BP control by sex in 2017-2020.

```{r}
nhanes_visualize(outcome = 'bp_control_accaha', 
                 exposure = 'demo_gender',
                 subset_variables = list("htn_accaha", "demo_pregnant"),
                 subset_values = list("Yes", c("No", "Missing")),
                 years = 'most_recent')[[1]]
```

### Proportion with BP control by race/ethnicity in 2017-2020.

```{r}
nhanes_visualize(outcome = 'bp_control_accaha', 
                 exposure = 'demo_race',
                 subset_variables = list("htn_accaha", "demo_pregnant"),
                 subset_values = list("Yes", c("No", "Missing")),
                 years = 'most_recent')[[1]]
```

