---
title: "Blood Pressure (BP) Control"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Blood Pressure (BP) Control}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}

knitr::spin_child("aaa.R")

```


```{r, include = FALSE}

standard_weights <- c(26.4, 43.5, 17.0, 13.2)
last_3 <- c("2013-2014", "2015-2016", "2017-2020")
outcome_variable <- 'bp_control_accaha'
outcome_text <- "BP control"

subset_calls <- 
 list("demo_pregnant" = c("No", "Missing"), 
      "htn_accaha" = "Yes")

subset_labs <- c("Not pregnant", "With hypertension")

```

**P1** `r outcome_text` is important because...

## `r outcome_text` overall

**P2** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot(standard_weights = standard_weights)
```


### Among those using antihypertensive medication

**P3** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot(subset_addons = list("bp_med_use" = "Yes"),
          standard_weights = standard_weights)
```


## `r outcome_text` by gender

**P4** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot(group_variable = 'demo_gender',
          standard_weights = standard_weights)
```


### Among those using antihypertensive medication

**P5** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot(group_variable = 'demo_gender',
          subset_addons = list("bp_med_use" = "Yes"),
          standard_weights = standard_weights)
```


## `r outcome_text` by age group

**P6** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot(group_variable = 'demo_age_cat',
          time_values = last_3)
```


### Among those using antihypertensive medication

**P7** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}

make_plot(group_variable = 'demo_age_cat',
          time_values = last_3,
          subset_addons = list("bp_med_use" = "Yes"),
          standard_weights = standard_weights)
```


## `r outcome_text` by race/ethnicity

**P8** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot(group_variable = 'demo_race',
          time_values = last_3,
          standard_weights = standard_weights)
```


### Among those using antihypertensive medication

**P9** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot(group_variable = 'demo_race',
          time_values = last_3,
          subset_addons = list("bp_med_use" = "Yes"),
          standard_weights = standard_weights)
```


## `r outcome_text` definition

For this analysis, our definition of `r outcome_text` was:

> `r text_vignette(get_variable_description('bp_control_accaha'))`

## Who is included in this analysis

`r cardioStatsUSA:::describe_module_sample('htn')` To analyze `r outcome_text`, we restricted the sample to non-pregnant adults with hypertension, which was defined as:

> `r text_vignette(get_variable_description('htn_accaha'))`

After these exclusions, a total of 26,766 participants were included for the current analysis.

`r cardioStatsUSA:::tabulate_module_sample('htn', subset_calls, subset_labs)`

## Age adjustment

For age adjustment in this analysis, we set the age distribution for the standard population to represent US adults with hypertension from 1999 to 2020: `r cardioStatsUSA:::describe_weights(standard_weights)`

## How were these results created?

EMBED YOUTUBE VIDEO HERE
