---
title: "Antihypertensive medication"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Antihypertensive medication}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup, include = FALSE}

knitr::spin_child("aaa.R")

```


```{r, include = FALSE}

standard_weights <- c(26.4, 43.5, 17.0, 13.2)
last_3 <- c("2013-2014", "2015-2016", "2017-2020")

outcome_variable <- 'bp_med_use'
outcome_text <- "Antihypertensive medication use"
outcome_text_lowercase <- "antihypertensive medication use"

subset_calls <- 
 list("demo_pregnant" = c("No", "Missing"))

subset_labs <- c("Not pregnant")

subset_htn <- list('htn_accaha' = 'Yes')

```

Randomized trials have demonstrated that antihypertensive medications lower blood pressure and prevent cardiovascular disease and mortality.

## `r outcome_text` in the overall US population

The percentage of US adults with hypertension that are taking blood pressure lowering medication increased from 1999-2000 to 2009-2010.  However, the percentage has not increased from 2009-2010 through 2017-2020. 

```{r}
make_plot(standard_weights = standard_weights)
```

### Among those with hypertension

```{r}
make_plot(subset_addons = subset_htn,
          standard_weights = standard_weights)
```

## `r outcome_text` by gender

Among US adults with hypertension, women are more likely to take antihypertensive medication compared with men.  However, there is a treatment gap with many women and men with hypertension not taking antihypertensive medication.

```{r}
make_plot(group_variable = 'demo_gender',
          standard_weights = standard_weights)
```

### Among those with hypertension

```{r}
make_plot(subset_addons = subset_htn,
          group_variable = 'demo_gender',
          standard_weights = standard_weights)
```

## `r outcome_text` by age group

The percentage of US adults with hypertension that is taking antihypertensive medication is higher at older age.  In 2017-2020, only about 1 in 5 US adults 18 to 44 years of age with hypertension was taking antihypertensive medication.

```{r}
make_plot(group_variable = 'demo_age_cat',
          time_values = last_3,
          standard_weights = standard_weights)
```

### Among those with hypertension

```{r}
make_plot(subset_addons = subset_htn,
          group_variable = 'demo_age_cat',
          time_values = last_3,
          standard_weights = standard_weights)
```

## `r outcome_text` by race/ethnicity

Among US adults with hypertension, non-Hispanic Black adults are more likely to take antihypertensive medication compared with non-Hispanic White and Asian adults and Hispanic adults. 
```{r}
make_plot(group_variable = 'demo_race',
          time_values = last_3,
          standard_weights = standard_weights)
```

### Among those with hypertension

```{r}
make_plot(subset_addons = subset_htn,
          group_variable = 'demo_race',
          time_values = last_3,
          standard_weights = standard_weights)
```

## `r outcome_text` definition

For this analysis, our definition of `r outcome_text_lowercase` was:

> `r text_vignette(get_variable_description(outcome_variable))`

## Who is included in this analysis

`r cardioStatsUSA:::describe_module_sample('htn')` Last, we restricted the sample to non-pregnant adults.

After these exclusions, a total of 54102 participants were included for the current analysis.

`r cardioStatsUSA:::tabulate_module_sample('htn', subset_calls, subset_labs)`

## Age adjustment

For age adjustment in this analysis, we set the age distribution for the standard population to represent US adults from 1999 to 2020: `r cardioStatsUSA:::describe_weights(standard_weights)`

```{r finale}
knitr::spin_child("footer.R")
```

