---
title: "cardioStatsUSA"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cardioStatsUSA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`cardioStatsUSA` aims to provide a platform for exploration of the National Health and Nutrition Examination Survey (NHANES) data. 

- We recommend new users start by using our shiny application to get a sense of what `cardioStatsUSA` can do. An example use of the application is provided in the instructional video below.

  ```{r, echo = FALSE}
  vembedr::embed_url("https://www.youtube.com/watch?v=oMporQuiodo")
  ```

- To automate the web application using code, we recommend reading more about the exported functions from `cardioStatsUSA` and its NHANES data in the [documentation](https://jhs-hwg.github.io/cardioStatsUSA/reference/index.html).

- To extend the web application using your own data and code, we recommend reading our vignette on [extending the web application](https://jhs-hwg.github.io/cardioStatsUSA/articles/modules.html) and also check out the videos provided in [this vignette](https://jhs-hwg.github.io/cardioStatsUSA/articles/replicate_nchs_2017.html) where I extend the application to replicate results from a prior study.


```{r finale, echo=FALSE}
knitr::spin_child("footer.R")
```
