---
title: "Hypertension"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Hypertension}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r child = '_aaa.Rmd'}

```


```{r, include = FALSE}

age_wts <- c(49.3, 33.6, 10.1, 7.0)
last_3 <- c("2013-2014", "2015-2016", "2017-2020")
outcome_variable <- 'htn_accaha'
outcome_text <- "Hypertension"
outcome_text_lowercase <- "hypertension"

subset_calls <- 
 list("demo_pregnant" = c("No", "Missing"))

subset_labs <- c("Not pregnant")

make_plot <- function(group_variable = NULL,
                      time_values = 'all',
                      subset_addons = NULL,
                      outcome_stats = 'percentage',
                      ...){

 
 .subset_calls <- c(subset_calls, subset_addons)
 
 plotly_vignette(
  nhanes_visualize(
   data = nhanes_data,
   key = nhanes_key,
   outcome_variable = outcome_variable,
   outcome_stats = outcome_stats,
   group_variable = group_variable,
   subset_calls = .subset_calls,
   time_values = time_values,
   title = "",
   age_wts = age_wts, 
   ...)
 )
 
}


```

**P1** `r outcome_text` is important because...

## `r outcome_text` overall

**P2** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot()
```

## `r outcome_text` by gender

**P4** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot(group_variable = 'demo_gender')
```

## `r outcome_text` by age group

**P6** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot(group_variable = 'demo_age_cat',
          time_values = last_3)
```

## `r outcome_text` by race/ethnicity

**P8** 1-2 sentences about the results. Here is some filler text for the second sentence
```{r}
make_plot(group_variable = 'demo_race',
          time_values = last_3)
```


## `r outcome_text` definition

For this analysis, our definition of `r outcome_text_lowercase` was:

> `r clean_text(get_variable_description(outcome_variable))`

## Who is included in this analysis

`r cardioStatsUSA:::describe_module_sample('htn')` To analyze `r outcome_text`, we restricted the sample to non-pregnant adults.

After these exclusions, a total of 54102 participants were included for the current analysis.

`r cardioStatsUSA:::tabulate_module_sample('htn', subset_calls, subset_labs)`

## Age adjustment

For age adjustment in this analysis, we set the age distribution for the standard population to represent US adults from 1999 to 2020: `r cardioStatsUSA:::describe_age_wts(age_wts)`

## How were these results created?

EMBED YOUTUBE VIDEO HERE
