---
title: "Prevalence of hypertension, 2017 ACC/AHA definition"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Prevalence of hypertension, 2017 ACC/AHA definition}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.height = 6,
  fig.width = 7.9,
  echo = FALSE
)
```

```{r setup}
library(cardioStatsUSA)
```

## Who is included in this analysis

## Hypertension

Hypertension is a major risk factor for cardiovascular disease. More cardiovascular disease events in the United States have been attributed to hypertension than any other modifiable risk factor.

## Hypertension (2017 ACC/AHA BP guideline definition)

The 2017 American College of Cardiology and American Heart Association (ACC/AHA) Guideline for the Prevention, Detection, Evaluation, and Management of High Blood Pressure (BP) in Adults defines hypertension as having a systolic BP ≥ 130 mm Hg or a diastolic BP ≥ 80 mm Hg.

### Prevalence by calendar year.

```{r}
nhanes_visualize(outcome = 'htn_accaha', 
                 years = 'all')[[1]]
```

### Prevalence by age group in 2017-2020.

```{r}
nhanes_visualize(outcome = 'htn_accaha',
                 exposure = 'demo_age_cat',
                 years = 'most_recent')[[1]]
```

### Prevalence by sex in 2017-2020.

```{r}
nhanes_visualize(outcome = 'htn_accaha',
                 exposure = 'demo_gender',
                 years = 'most_recent')[[1]]
```


### Prevalence by race/ethnicity in 2017-2020.

```{r}
nhanes_visualize(outcome = 'htn_accaha',
                 exposure = 'demo_race',
                 years = 'most_recent')[[1]]
```
