---
title: "Replicating analysis from Muntner et al, 2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Replicating analysis from Muntner et al, 2020}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(testthat)
knitr::spin_child('aaa.R')
```

`r cardioStatsUSA:::describe_replicate_intro("a prior study in the *Journal of the American Medical Association*")`

## Replicate with shiny application

The video below shows how Table 2 can be replicated using our web application.

```{r}
vembedr::embed_url("https://www.youtube.com/watch?v=EQe7feUjNuo")
```

The video below shows how eTable 1 can be replicated using our web application.

```{r}
vembedr::embed_url("https://www.youtube.com/watch?v=Knc-Os7yUdQ")
```

## Replicate with code

`r cardioStatsUSA:::describe_replicate_with_code()` 

```{r}
knitr::spin_child("../tests/testthat/test-replicate_muntner_jama_2020.R")
```

```{r finale}
knitr::spin_child("footer.R")
```
