---
title: "Replicating analysis from the NCHS data brief, 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Replicating analysis from the NCHS data brief, 2017}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(testthat)
knitr::spin_child('aaa.R')
```

`r cardioStatsUSA:::describe_replicate_intro("a report from the National Center for Health Statistics (NCHS) data brief")`

## Replicate with shiny application

The video below shows how Figure 1 can be replicated using our web application.

```{r}
vembedr::embed_url("https://www.youtube.com/watch?v=FwxdEfyTiIQ")
```


The video below shows how Figure 2 can be replicated using our web application.

```{r}
vembedr::embed_url("https://www.youtube.com/watch?v=DzAhLVP0AaY")
```

## Replicate with code

`r cardioStatsUSA:::describe_replicate_with_code()` 

```{r}
knitr::spin_child("../tests/testthat/test-replicate_cdc_report.R")
```

```{r finale}
knitr::spin_child("footer.R")
```
