---
title: "Replicating analysis from the NCHS data brief, 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Replicating analysis from the NCHS data brief, 2017}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(testthat)
knitr::spin_child('aaa.R')
```

`r cardioStatsUSA:::describe_replicate_intro("a report from the National Center for Health Statistics (NCHS) data brief")`

## Replicate with shiny application

The video below shows how Figure 1 can be replicated using our web application.

```{r}
vembedr::embed_url("https://www.youtube.com/watch?v=FwxdEfyTiIQ")
```


The video below shows how Figure 2 can be replicated using our web application.

```{r}
vembedr::embed_url("https://www.youtube.com/watch?v=DzAhLVP0AaY")
```

The code used in the video to run the application with a different age variable is provided below for interested users:

```{r, eval=FALSE, echo = TRUE}

library(cardioStatsUSA)
library(data.table)
library(magrittr)

# Make a copy of the NHANES data
nhanes_data_test <- copy(nhanes_data)

# modify the age groups prior to running the app
nhanes_data_test[
 , demo_age_cat := cut(demo_age_years,
                       breaks = c(18, 39, 59, Inf),
                       labels = c("18-39", "40-59", "60+"),
                       include.lowest = TRUE)
]

#' Include the same cohort as the CDC report

nhanes_data_test <- nhanes_data_test %>%
 # exclude pregnant women
 .[demo_pregnant == 'No' | is.na(demo_pregnant)] %>%
 # exclude participants missing both SBP and DBP
 .[!(is.na(bp_dia_mean) & is.na(bp_sys_mean))]


# don't include cholesterol module (cholesterol is in development)
nhanes_key_test <- nhanes_key[module != 'chol']

# important: if 'module' is included as a column in your key,
# then the app will automatically subset your cohort to include
# NHANES participants in the module that your outcome variable is in.
# We don't want to do that here, since the cohort analyzed by the CDC 
# didn't have the same exclusion criteria as the cohort we analyze by
# default in the app. So, the simple fix is to delete the module column:
nhanes_key_test$module <- NULL


app_run(nhanes_data = nhanes_data_test,
        nhanes_key = nhanes_key_test)


```


## Replicate with code

`r cardioStatsUSA:::describe_replicate_with_code()` 

```{r}
knitr::spin_child("../tests/testthat/test-replicate_cdc_report.R")
```

```{r finale}
knitr::spin_child("footer.R")
```
